%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Preamble									%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\documentclass{bibliography}

	\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
	\usepackage{tipa}
	\usepackage{hyperref}
	\usepackage{amsmath}
	\usepackage{tabularx}
	\usepackage{enumitem} % For customizing item spacing

	\newcolumntype{L}{>{\raggedright\arraybackslash}X}

	\newcommand{\cvpub}[4]{
		\item
		\begin{tabularx}{\textwidth}[t]{@{}X@{} r@{}}
			\vtop{
				\hsize=0.85\textwidth
				#1
				\vfill
				{\scriptsize\emph{Keywords:} #2}
			} &
			\hspace{-3.5em}
			\makebox[0pt][r]{
				\begin{tabular}[t]{@{}r@{}}
					\href{#3}{[doi]} \\
					\href{#4}{[pdf]}
				\end{tabular}
			}
		\end{tabularx}
	}

	\hypersetup{
	    colorlinks=true,
	    linkcolor=blue,
	    urlcolor=blue,
	    % filecolor=magenta,      
	    % urlcolor=cyan,
	    % pdftitle={Overleaf Example},
	    % pdfpagemode=FullScreen,
    }

	\name{\LARGE{
		G. Lynn Kurteff, PhD, MS-SLP
	}}% Your name

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications 								%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{rSection}{Peer-reviewed Journal Articles}

		\begin{rSubsection_pubs}{}{}{}{}
			\cvpub
				{Zhao, L., Silva, A.B., \textbf{Kurteff, G.L.}, \& Chang, E.F. (2025). \emph{Inhibitory control of speech production in the human premotor frontal cortex.} Nature Human Behavior.}
				{ECoG, cortical stimulation mapping, speech production, speech arrest}
				{https://doi.org/10.26153/tsw/56510}
				{https://kurteff.github.io/assets/pdf/zhao2025manuscript.pdf}

			\cvpub
				{\textbf{Kurteff, G.L.}, Field, A.M., Asghar, S., Tyler-Kabara, E.C., Clarke, D., Weiner, H.L., Anderson, A.E., Watrous, A., Buchanan, R.J., Modur, P.N., \& Hamilton, L.S. (2024). \emph{Spatiotemporal mapping of auditory onsets during speech production.} Journal of Neuroscience.}
				{sEEG, ECoG, speech production, speech perception, auditory feedback, insular auditory field}
				{http://dx.doi.org/10.1523/JNEUROSCI.1109-24.2024}
				{https://kurteff.github.io/assets/pdf/kurteff2024manuscript.pdf}

			\cvpub
				{\textbf{Kurteff, G.L.}, Lester-Smith, R.A., Martinez, A., Currens, N., Holder, J., Villarreal, C., Mercado, V.R., Truong, C., Huber, C., Pokharel, P., \& Hamilton, L.S. (2023). \emph{Speaker-induced suppression in EEG during a naturalistic reading and listening task.} Journal of Cognitive Neuroscience.}
				{EEG, speech production, speech perception, auditory feedback}
				{https://doi.org/10.1162/jocn_a_02037}
				{https://kurteff.github.io/assets/pdf/kurteff2023manuscript.pdf}
			
			\cvpub
				{Levy, D.F., Silva, A.B., Scott, T., Liu, J., Harper, S., Zhao, L., Hullett, P., \textbf{Kurteff, G.}, Andrews, J., Wilson, S.M., Leonard, M., \& Chang, E.F. (2023). \emph{Apraxia of speech with phonological alexia and agraphia following resection of the left middle precentral gyrus.} Journal of Neurosurgery: Case Lessons.}
				{case study, lesion-symptom mapping, apraxia of speech, speech and language assessment, neurosurgery}
				{https://doi.org/10.3171/case22504}
				{https://kurteff.github.io/assets/pdf/levy2023manuscript.pdf}
			
			\cvpub
				{Ammanuel, S., Almeida, N.C., \textbf{Kurteff, G.}, Kakaizada, S., Molinaro, A., Berger, M.S., Chang, E.F., \& Hervey-Jumper, S.L. (2021). \emph{Natural language assessment correlates with health-related quality of life in adult glioma patients.} Journal of Neuro-Oncology.}
				{speech sample analysis, neurosurgery}
				{https://doi.org/10.1093/neuonc/noaa215.575}
				{https://kurteff.github.io/assets/pdf/ammanuel2022manuscript.pdf}
			
			\cvpub
				{Chang, E.F., \textbf{Kurteff, G.}, Andrews, J., Briggs, R.G., Conner, A.K., Battiste, J.D., \& Sughrue, M.E. (2020). \emph{Pure apraxia of speech after focal surgical resection of area 55b in dorsal premotor cortex.} Neurosurgery.}
				{case study, lesion-symptom mapping, apraxia of speech, speech and language assessment, neurosurgery}
				{http://doi.org/10.1093/neuros/nyaa002}
				{https://kurteff.github.io/assets/pdf/chang2020manuscript.pdf}
			
			\cvpub
				{De Witte, E., Piai, V., \textbf{Kurteff, G.}, Cai, R., Mari{\"e}n, P., Dronkers, N., Chang, E.F., \& Berger, M.S. (2018). \emph{A valid alternative for in-person language assessments in brain tumor patients: Feasibility and validiy measures of the new TeleLanguage test.} Neuro-Oncology Practice.}
				{speech and language assessment, aphasia, neurosurgery}
				{http://doi.org/10.193/nop/npy020}
				{https://kurteff.github.io/assets/pdf/dewitte2019manuscript.pdf}
		
			\cvpub
				{Chang, E.F., \textbf{Kurteff, G.}, \& Wilson, S.M. (2018). \emph{Selective interference with syntactic encoding during sentence production by direct electrocortical stimulation of the inferior frontal gyrus.} Journal of Cognitive Neuroscience.}
				{cortical stimulation mapping, speech production, expressive syntax}
				{http://doi.org/10.1162/jocn_a_01215}
				{https://kurteff.github.io/assets/pdf/chang2018manuscript.pdf}
		\end{rSubsection_pubs}
	\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% In prep 									%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{rSection}{Journal Articles Submitted/in Preparation/in Revision}
		
		\begin{rSubsection_list}{}{}{}{}
			\item{
				\textbf{Kurteff, G.L.}, Walker, G.M., Fridriksson, J., \& Hickok, G. (in prep). \emph{Mapping of critical prosodic and phonetic networks in post-stroke apraxia of speech.}\\
				{\scriptsize\emph{Keywords:} lesion-symptom mapping, apraxia of speech}
			}
			\item{
				Walker, G.M., \textbf{Kurteff, G.L.}, Hussain, A., Fridriksson, J., \& Hickok, G. (in prep). \emph{Critical-network lesion-symptom mapping.}\\
				{\scriptsize\emph{Keywords:} lesion-symptom mapping}
			}
			\item{
				Walker, G.M., \textbf{Kurteff, G.L.}, Fridriksson, J., \& Hickok, G. (in prep). \emph{Distinct sources of nonword errors in post stroke aphasia.}\\
				{\scriptsize\emph{Keywords:} psychometric modeling, aphasia, apraxia of speech, speech and language assessment, lesion-symptom mapping}
			}
			\item{
				\textbf{Kurteff, G.L.} \& Hamilton, L.S. (in prep). \emph{The human insular auditory field.}\\
				{\scriptsize\emph{Keywords:} literature review, insular auditory field}
			}
			\item{
				\textbf{Kurteff, G.L.}, Field, A.M., Asghar, S., Tyler-Kabara, E.C., Clarke, D., Weiner, H.L., Anderson, A.E., Watrous, A., Buchanan, R.J., Modur, P.N., \& Hamilton, L.S. (in prep). \emph{onsetProd: an intracranial sEEG dataset of naturalistic sentence production and perception.}\\
				{\scriptsize\emph{Keywords:} sEEG, ECoG, speech production, speech perception, dataset}
			}
		\end{rSubsection_list}
	\end{rSection}

% \vspace{2cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Posters 									%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{rSection}{Conference Presentations}
		\begin{rSubsection_list}{}{}{}{}

			\item{\textbf{Kurteff, G.L.}, Tyler-Kabara, E.C., Clarke, D., Weiner, H.L., Anderson, A.E., Watrous, A., Asghar, S., Field, A., \& Hamilton, L.S. (2024). \emph{Intracranial EEG Processing of Auditory Feedback in Perisylvian Cortex}. Poster session presented at the Annual Meeting of the Cognitive Neuroscience Society, Toronto, ON, Canada.}\\
			{\scriptsize\emph{Keywords:} sEEG, ECoG, speech production, speech perception, auditory feedback, insular auditory field}

			\item{Hamilton, L.S., Asghar, S., Desai, M,, \textbf{Kurteff, G.L.}, Field, A., Nussbaum, N.L., Clarke, D., Tyler-Kabara, E.C., Anderson, A., \& Weiner, H.L. (2023). \emph{Utilizing Clinical Intracranial Epilepsy Monitoring Infrastructure for Basic Science Research of Speech and Language Development}. Poster session presented at the Annual Meeting of the Child Neurology Society, Vancouver, BC, Canada.}\\
			{\scriptsize\emph{Keywords:} sEEG, epilepsy, methods}
			
			\item{\textbf{Kurteff, G.}, \& Hamilton, L.S. (2022). \emph{Stereo EEG mapping of sensorimotor responses to self-generated speech.} Poster session presented at the Annual Meeting of the Texas Speech-Language Hearing Association, Fort Worth, TX; Association for Research in Otolaryngology, virtual meeting due to COVID-19.}\\
			{\scriptsize\emph{Keywords:} sEEG, speech production, speech perception, auditory feedback}

			\item{Cheng, C., Young, N., Teplansky, K., \textbf{Kurteff, G.}, Salman, R., Mau, T., \& Wang, J. (2022). \emph{Fricative production in laryngeal, electrolaryngeal, and tracheoesophageal speech.} Poster session presented at the biannual meeting of the Conference on Motor Speech, Charleston, SC.}\\
			{\scriptsize\emph{Keywords:} articulatory phonetics, voice, alaryngeal speech}

			\item{\textbf{Kurteff, G.}, \& Hamilton, L.S. (2021). \emph{Encoding of phonological features in intracranial recordings of human speech cortex during a dual perception-production task}. Poster session presented at the Annual Meeting of Advances and Perspectives in Auditory Neuroscience, virtual meeting due to COVID-19.}\\
			{\scriptsize\emph{Keywords:} sEEG, speech production, speech perception}

			\item{\textbf{Kurteff, G.}, Martinez, A., Currens, N., Holder, J., Mercado, V., Truong, C., Huber, C., Pokharel, P., \& Hamilton, L.S. (2020a; 2021b). \emph{Methods for Investigating Continuous Speech Production and Perception with EEG.} Poster session presented at a. the Annual Meeting of the Society for Neurobiology of Language; b. Texas Speech-Language Hearing Association, virtual meetings due to COVID-19.}\\
			{\scriptsize\emph{Keywords:} EEG, EMG, speech production, speech perception, methods}

			\item{\textbf{Kurteff, G.}, Fox, N.P., Dronkers, N.F., Desai, M., Shafi, A., \& Chang, E.F. (2019). \emph{Behavioral and neuroanatomical description of stimulation-induced speech arrest.} Poster session presented at the Annual Meeting of the Cogntive Neuroscience Society, San Francisco, CA, USA.}\\
			{\scriptsize\emph{Keywords:} cortical stimulation mapping, speech production, speech arrest}

			\item{Chang, E.F., \textbf{Kurteff, G.}, \& Wilson, S.M. (2017). \emph{Selective interference with syntactic encoding during sentence production by direct electrocortical stimulation of the inferior frontal gyrus.} Poster session presented at the Annual Meeting of the Society for the Neurobiology of Language, Baltimore, MD, USA.}\\
			{\scriptsize\emph{Keywords:} cortical stimulation mapping, speech production, expressive syntax}

			\item{De Witte, E., Piai, V., \textbf{Kurteff, G.}, Cai, R., Berger, M.S., Chang, E.F., \& Dronkers, N. (2016). \emph{Usability and validity of a phone battery to assess language functions in brain tumor patients undergoing awake surgery.} Poster session presented at the Annual Meeting of the Academy of Aphasia, Llandudno, Wales; UK and Society of Neurooncology, Scottsdale, AZ, USA. }\\
			{\scriptsize\emph{Keywords:} speech and language assessment, cortical stimulation mapping, aphasia, neurosurgery}
		\end{rSubsection_list}
	\end{rSection}

% \vspace{2cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thesis & diss								%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{rSection}{Theses and Dissertations}
		\begin{rSubsection_pubs}{}{}{}{}
			\cvpub
				{\textbf{Kurteff, G.L.} (2024). \emph{Cortical Suppression of Auditory Feedback during Speech Production and Perception}. PhD dissertation.}
				{sEEG, ECoG, EEG, EMG, speech production, speech perception, auditory feedback, insular auditory field}
				{https://doi.org/10.26153/tsw/56510}
				{https://kurteff.github.io/assets/pdf/kurteff2024dissertation.pdf}
			\cvpub
				{\textbf{Kurteff, G.} (2020). \emph{Modulation of neural responses to naturalistic speech production and perception}. Masters thesis.}
				{EEG, EMG, speech production, speech perception, auditory feedback}
				{http://dx.doi.org/10.26153/tsw/14461}
				{https://kurteff.github.io/assets/pdf/kurteff2020thesis.pdf}
		\end{rSubsection_pubs}
	\end{rSection}

\emph{Document last compiled: \today}

\end{document}
